---
title: "DNA Hydroxymethylation in Hepatocellular Carcinoma"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{DNA Hydroxymethylation in Hepatocellular Carcinoma}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
  %\VignetteDepends{purrr,blogdown,dplyr}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
#library(omicScaleAnalyticR)
```

```{r echo=FALSE, include=F}
blogdown::shortcode('tweet', '922545181634768897')
```

<blockquote class="twitter-tweet"><p lang="en" dir="ltr">I’m embarrassed to admit that, while I aspire to be a tidyverser, I remain a somewhat desiccated baseR-er. 😳 <a href="https://twitter.com/hashtag/rstats?src=hash&amp;ref_src=twsrc%5Etfw">#rstats</a> <a href="https://t.co/lxEFfoU8tw">https://t.co/lxEFfoU8tw</a></p>&mdash; Karl Broman (@kwbroman) <a href="https://twitter.com/kwbroman/status/922545181634768897?ref_src=twsrc%5Etfw">October 23, 2017</a></blockquote> <script async src="https://platform.twitter.com/widgets.js" charset="utf-8"></script>

```{r getTiduverseFncs, include=F}

 # map_
 library(purrr)
 map_fcns <- ls("package:purrr", patt='^map_')

 # merge
 library(dplyr)
 join_fcns <- ls("package:dplyr", patt='_join$')


 # install_
 #library(devtools)
 #install_fcns <- ls("package:devtools", patt='install')

```

<br/>
<br/>

There are `r length(map_fcns)` **map** functions in the `purrr` package:  

* `r map_fcns`  

The are `r length(join_fcns)` **join** functions in the `dplyr` package:  

* `r join_fcns`  

I would guess that over 99% of use cases are perfectly well covered by one or two lines
of code invoking either the `base::lapply` or the `base::merge` function.


<!-- To run
# nohup Rscript -e "knitr::knit2html('HCC_5hmc.Rmd')" > HCC_5hmc.log  &

# Or
# nohup Rscript -e "rmarkdown::render('HCC_5hmc.Rmd')" > HCC_5hmc.log  &

-->

